---
title: 'Week 4: Board Games'
author: "Jose F. Grillo"
date: "25/1/2022"
output:
  html_document:
    toc:  TRUE
    toc_float: TRUE
editor_options: 
  chunk_output_type: console
---

<style> body {text-align: justify} </style>

```{r Styling, include=FALSE}

options(encoding = 'UTF-8')

```

## Loading the data frame

We first start by loading the dataframe using the recommended input from the [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-01-25/readme.md) webpage:

```{r Loading the data}

#Packages
require(tidyverse)
require(ggtext)

#Downloading the data
tuesdata <- tidytuesdayR::tt_load('2022-01-25')

#Creating the separate dataframes
ratings <- tuesdata$ratings
details <- tuesdata$details

```


## Lollipop chart with the average of ratings

After reviewing the data and finding out some interesting patterns that can be explored at a later date, I decided to create a simple lollipop chart with the ratings of the board games of the 21^st^ century.

```{r Lollipop chart}

#Average rating
AVG_rating <- ratings %>%
  filter(year >= 2000 & year <= 2021) %>%
  summarize(AVG = mean(average), AVG_Bayes = mean(bayes_average))

#Lollipop plot
ratings %>%
  filter(year >= 2000 & year <= 2021) %>%
  group_by(year) %>%
  summarize(Number = n(), Avg = mean(average), Avg_bayes = mean(bayes_average)) %>%
  
  ggplot() +
#Creating the segmented overall average line 
  geom_vline(aes(xintercept = 6.526118), 
             color = "red", 
             linetype = 2, 
             size = 0.5) +
#Creating the line of the lollipop
  geom_segment(aes(x = Avg, xend = 6.526118, y = year, yend = year)) +
#Creating the "point" of the lollipop
  geom_point(aes(x = Avg, y = year),
             size = 10,
             alpha = 0.8) +
#Creating the label of the lollipop
  geom_text(aes(x = Avg, y = year, label = signif(Avg, 3)),
            color = "white",
            size = 3.5) +
#Modifying the labs and adding the title, subtitle and caption
  labs(x = NULL, y = NULL, 
       title = "Are board games getting better in the new\nmillennium?", 
       subtitle = "The mean yearly rating of the considered board games\nis higher than the overall average since 2016", 
       caption = "**Plot:** @JF_Grillo_Bio | **Data:** Kaggle & Board Games Geek (via TidyTuesday)") +
#Modifying the x axis (breaks)
  scale_x_continuous(breaks = c(6.0, 6.25, 6.5, 6.75, 7.0, 7.25)) +
#Modifying the y axis (breaks)
  scale_y_continuous(breaks = 2000:2021) +
#Creating the annotations  
  geom_curve(aes(
           x = 6.526118,
           xend = 6.7, 
           y = 2006.2,
           yend = 2004.5),
           arrow = arrow(length = unit(1.78, "mm")), 
           size = 0.4,
           curvature = 0.3,
           color = "red") +
  
  annotate(geom = "text",
           x = 7.05,
           y = 2004.5,
           #size = ,
           color = "black",
           lineheight = 0.9,
           label = "Overall average rating = 6.53") +
  
  geom_curve(aes(
           x = 6.38,
           xend = 6.2, 
           y = 2014,
           yend = 2016),
           arrow = arrow(length = unit(1.78, "mm")), 
           size = 0.4,
           curvature = -0.3) +
  
  annotate(geom = "text",
           x = 6.155,
           y = 2016.5,
           #size = ,
           color = "black",
           lineheight = 0.9,
           label = "Average rating") +
#Assigning the theme
  theme_minimal() +
#Modifying the theme
  theme(plot.title = element_text(size = 18, face = "bold"),
        plot.subtitle = element_text(size = 15),
        plot.caption = element_markdown(),
        plot.title.position = "plot",
        plot.background = element_rect("white"),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_blank(),
        panel.grid = element_blank(),
        plot.margin = margin(t = 15, r = 15, b = 15, l = 15)
        )

#ggsave(filename = "TidyTuesday_Boardgame.png", width = 15, height = 20, units = "cm", dpi = 2000)

```

